Predicting the effect of candidate interventions for mitigating disease spread in asymmetric mixing metapopulations

### 2024-07-18 ms.tex
added equations and started disc outline

\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[sorting=none, style=numeric-comp]{biblatex}
\addbibresource{../library.bib}
\usepackage{bookmark}

\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}

@@

\caption{We can model the relevant groups for mixing as either village
residence or ethnicity. Transmission, mixing, and mobility parameters
would be set accordingly. The \(C_g\) parameters would be reduced if
economic aid were allocated to keep group \(g\) on the Reserve during
outbreaks.}

@@

{\centering \includegraphics[width=0.95\textwidth,height=\textheight]{Figures/ResultsSketch.pdf}

@@

@@

>>>>

\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[sorting=none, style=numeric-comp]{biblatex}
\addbibresource{../library.bib}
\usepackage{bookmark}
\usepackage{xcolor}
\definecolor{myorange}{RGB}{240, 96, 0}
\newcommand{\mt}[1]{{\textcolor{myorange} {({\tiny MT:} #1)}}}
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}

@@

\caption{\mt{UPDATE THIS CAPTION AND THE FIGURE TO MATCH EQUATIONS. ADD PARAMETERS TABLE.}
  We can model the relevant groups for mixing as either village
residence or ethnicity. Transmission, mixing, and mobility parameters
would be set accordingly. The \(C_g\) parameters would be reduced if
economic aid were allocated to keep group \(g\) on the Reserve during
outbreaks.}

@@

{\centering \includegraphics[width=0.95\textwidth,height=\textheight]{Figures/ResultsSketch_ReductionByGroup.pdf}

@@

{\centering \includegraphics[width=0.95\textwidth,height=\textheight]{Figures/ResultsSketch_ByStrategy.pdf}

\caption{We hypothesize that overall reduction in disease incidence ($\Delta I$, y-axis)  depends on 
strategy to distribute the total aid to reduce travel between Dourados Reserve and city ($\gamma$, x-axis).}

@@

\begin{itemize}
  \item 
    Application to other problematic diseases in the Reserve, e.g., TB, STDs,\ldots 
  \item
    The data is not necessarily representative and we had to use educated guesses
    for mixing parameters.
\end{itemize}
